### 2021-03-14 chapters/sections/1-context.tex
backup

Today, many services are accessible through the internet. Especially during the COVID-19 pandemic, stores had to switch to online trade due to lockdowns. Online Service Providers (SP) often require customers to create user profiles in order to access their services. Management of personal information as well as interaction and communication between Service Provider and customer are often only possible through a web page or e-mail. It is time consuming to maintain even a small amount of user profiles: To change personal information, like an e-mail address, the web page of each Service Provider has to be accessed the correct credentials have to be submitted and the information has to be manually filled in each time.

@@

A currently relevant topic with an interesting approach for identity management is the German Online Access Law (Online Zugangs Gesetz - OZG). It requires German federal republic, each federal state and commune to provide administration portals for digital access to administrative services. Federal republic and each member state operate their individual user profile systems accessible through their administration portals.

The Online Access Law therefore constructs a system landscape which demonstrates the scenario of distributed partial identities on a small scale while maintaining the same problems as the private sector: Users have to create, maintain and login into multiple user profiles to access administrative services distributed across administration portals. To solve this problem, a solution for making OZG user profiles "interoperable" is in development. However, interoperable user profiles can not be accessed by the private sector.

>>>>

Today, many services are accessible through the internet. Especially during the COVID-19 pandemic, stores had to switch to online trade due to lockdowns. Even after lockdowns, customers might continue to favour e-commerce \cite{9076858}. Online Service Providers (SP) often require customers to create user profiles in order to access their services. Management of personal information as well as interaction and communication between Service Provider and customer are often only possible through a web page or e-mail. It is time consuming to maintain even a small amount of user profiles: To change personal information, like an e-mail address, the web page of each Service Provider has to be accessed the correct credentials have to be submitted and the information has to be manually filled in each time.

@@

A currently relevant topic with an interesting approach for identity management is the German Online Access Law (Online Zugangs Gesetz - OZG). It requires German federal republic, each federal state and commune to provide administration portals for digital access to administrative services \cite{ozg:general}. Federal republic and each member state operate their individual user profile systems accessible through their administration portals \cite{ozg:user_profiles_general}.

The Online Access Law therefore constructs a system landscape which demonstrates the scenario of distributed partial identities on a small scale while maintaining the same problems as the private sector: Users have to create, maintain and login into multiple user profiles to access administrative services distributed across administration portals. To solve this problem, a solution for making OZG user profiles "interoperable" is in development \cite{ozg:user_profiles_general}. However, interoperable user profiles can not be accessed by the private sector.

### 2021-03-14 chapters/sections/6-online_access_law.tex
backup

In 2017, the German government passed the Online Access Law (OZG) which requires federal republic and member states to execute the following regulations until 2022 \cite{BMI:OZG_Wortlaut}:

\paragraph{Digital availability of administrative services} An administrative service is the electronic processing of administrative procedures that are available from outside the governmental institution.  As it is not clear which administrative services exactly are included by the definition of the OZG, the Federal Ministry of the Interior Building and Community (Bundesministerium des Innern, für Bau und Heimat - BMI) created a catalogue \cite{BMI:Verwaltungsleistungen}. The OZG requires these services to be digitally available. As a guideline to what is considered sufficient availability, the BMI defined a maturity model \cite{BMI:Digitale_Services}.

\paragraph{Digital access to administrative services through administration portals of a portal network} Federal republic, each federal state and each commune must provide an administration portal. Portals of communes must be linked to the portal of the corresponding member state. Portals of federal republic and member states must be connected through a portal network. \cite{BMI:Portalverbund} Each portal must provide a "seek and find" feature, which enables users to find all administrative services provided by any administration portal \cite{Cotar:Drucksache_19/19089}.

\paragraph{Interoperable user profiles for accessing administrative services} Federal republic and member states must provide user profiles that can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services \cite{Cotar:Drucksache_19/19089}. The user profiles must be interoperable for every administration portal of the portal network.

>>>>

In 2017, the German government passed the Online Access Law (OZG) which requires federal republic and member states to execute the following regulations until 2022 \cite{ozg:regulations}:

\paragraph{Digital availability of administrative services} An administrative service is the electronic processing of administrative procedures that are available from outside the governmental institution.  As it is not clear which administrative services exactly are included by the definition of the OZG, the Federal Ministry of the Interior Building and Community (Bundesministerium des Innern, für Bau und Heimat - BMI) created a catalogue \cite{ozg:informationsplattform}. The OZG requires these services to be digitally available. As a guideline to what is considered sufficient availability, the BMI defined a maturity model \cite{ozg:maturity_model}.

\paragraph{Digital access to administrative services through administration portals of a portal network} Federal republic, each federal state and each commune must provide an administration portal. Portals of communes must be linked to the portal of the corresponding member state. Portals of federal republic and member states must be connected through a portal network. \cite{ozg:onlinegateway_general} Each portal must provide a "seek and find" feature, which enables users to find all administrative services provided by any administration portal \cite{ozg:onlinegateway_architecture}.

\paragraph{Interoperable user profiles for accessing administrative services} Federal republic and member states must provide user profiles that can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services. The user profiles must be interoperable for every administration portal of the portal network \cite{ozg:user_profiles_general}.
